---
title: "README"
author: "Soleil98"
date: "2023-01-26"
output:
  html_document:
    df_print: paged
---

# PIPS2023

## About

This repository contains three R functions that have been created as part of an 
assignment for the Programming in Psychological Science course at the UvA in 2023.


## The Functions
### remind_me()

The remind_me() function returns some things that are useful for myself to remember.
It does not take any arguments.

```{r remind_me, echo=TRUE}
source("remind_me_function.R")
remind_me()
```

### cheat()

The cheat() function tells the user the correct solution to questions from the 
third assignment of the course by printing to the console. It currently works 
for Q3.1.3, Q3.1.7 and Q3.1.11 of the assignment.

The exercise number must be entered as a string.

```{r cheat, echo=TRUE}
source("cheat_function.R")
cheat("Q3.1.3")
```

### make_art()

The make_art() function produces random artworks in R. It takes an optional 
argument which sets the seed for the randomly generated artwork to ensure its
reproducibility. As in the set.seed() function, make_art() can take any integer
numeric value.

```{r make_art, echo =TRUE}
source("make_art_function.R")
make_art(seed = 1382)
```


## Usage

To use the functions in RStudio, you can copy and run the code from the files in 
this repository (https://github.com/Soleil98/PIPS2023/tree/main) in RStudio. All
three functions run without any argument, but you can specify optional arguments
for cheat() and make_art() as explained above.




