---
title: "README"
author: "Soleil98"
date: "2023-01-26"
output:
  html_document:
    df_print: paged
  pdf_document: default
  word_document: default
---

# PIPS2023

## About

This repository contains three R functions that have been created as part of an assignment for the Programming in Psychological Science course at the UvA in 2023.

## The Functions

### remind_me()

The remind_me() function returns some things that are useful for myself to remember. It does not take any arguments.

```{r, echo=TRUE}
source("remind_me_function.R")
remind_me()
```

### cheat()

The cheat() function tells the user the correct solution to questions from the third assignment of the course by printing to the console. It currently works for Q3.1.3, Q3.1.7 and Q3.1.11 of the assignment.

The function takes the 'question_number' as an optional argument. The question number must be entered as a string. The default for 'question_number' is "Q3.1.3".

```{r, echo=TRUE}
source("cheat_function.R")
cheat("Q3.1.3")
```

### make_art()

The make_art() function produces random artworks in R. It takes the optional argument 'seed' which sets the seed for the randomly generated artwork to ensure its reproducibility. As the set.seed() function, make_art() can take any integer numeric value. Per default 'seed' = 13.

```{r, echo =TRUE}
source("make_art_function.R")
make_art(seed = 13)
```

## Usage

To use the functions in RStudio, you can copy and run the code from the files in this repository (<https://github.com/Soleil98/PIPS2023/tree/main>) in RStudio. All three functions run without any argument, but you can specify optional arguments for cheat() and make_art() as explained above.
